Manifold Destiny - or how to rig an election

### 2024-01-27 presentation.qmd
starwork
break

---
title: "Manifold Destiny - or how to rig an election"
subtitle: "Based upon the ideas developed by Edward K. Solomon"
format:
  revealjs: 
    smaller: true
    toc-depth: 1
    toc: true 
#webr: 
#  show-startup-message: true    # Disable displaying status of webR initialization
#  packages: ['dplyr','purrr','magrittr','data.table','tidyr'] # Install R packages on document open
##filters:
#- webr 
#footer: <https://lotariohw26.github.io/ManifoldDestiny/>
---

@@

Election outome
```{r, echo=F}
#sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
polynom::integral(round(polynom::polynomial(unname(pos_int_ex3))),c(0,1))
```
```{r}
knitr::knit_exit()
```

@@

- Loss function
  - $M(,)=$x+y$
    - Use: Linear, quadratic, cubic or quartic (all have analytical solutions)
    - Also: Euler rotation
  - System approach Demands mulitvariate Manifold Equations
    - Abc
    - Def
  - Constrain on implementation
    - Flipping votes on one mode
    - Vote registration until upper limit

>>>>

---
title: "Manifold Destiny - or how to rig an election"
subtitle: "Based upon the ideas developed by Edward K. Solomon"
format:
  revealjs: 
    smaller: true
    toc-depth: 1
    toc: true 
execute: 
  cache: false
#webr: 
#  show-startup-message: true    # Disable displaying status of webR initialization
#  packages: ['dplyr','purrr','magrittr','data.table','tidyr'] # Install R packages on document open
##filters:
#- webr 
#footer: <https://lotariohw26.github.io/ManifoldDestiny/>
---

@@

Election outome
```{r, echo=F}
#sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
polynom::integral(round(polynom::polynomial(unname(pos_int_ex3))),c(0,1))
```

@@

- Specify a loss function
  - $\sum_{p=1}^{P}(\alpha_p-\overline{\alpha})^2$
- $M(,)=$x+y$
  - Use: Linear, quadratic, cubic or quartic (all have analytical solutions)
  - Also: Euler rotation
- System approach Demands mulitvariate Manifold Equations
  - Univariate manifold Equation
  - Multivariate Manifold Equations
- Constrain on implementation
  - Flipping votes on one mode
  - Vote registration until upper limit
